Predicting the PCG PSeudo-Random Number Generator In Practice

### 2020-05-28 article/main.tex
l=0 + SVP

The LCG have been largely studied. This is why we know techniques to recover internal states knowing only upper or lower bits of the output, see \cite{Boyar1989}. A particular LCG is the Lehmer's generator \cite{Lehmer} \todo{je sais pas écire la référence dans bibtex}, where the multiplier \(a\) is known and the increment is zero.

@@

In this article, we will only use the Babai's rounding when \(k = 128-\ell\) and when we know the \(6\) upper bit of our Lehmer's generator. Hence \(\lVert T-U \rVert \leqslant \sqrt{n}2^{122-\ell} \). So, if we fix \(\ell\) we can search for the minimum \(n\) such that \[2\sqrt{n}2^{122-\ell} \leqslant \lambda_1(L(128-\ell,n))\].

\begin{table}
  \centering
    \begin{tabular}{|c|c|}
	\hline
	\(\ell\)  & minimum \(n\) \\
	\hline
	11 & 39 \\
	12 & 38 \\
	13 & 38 \\
	\hline
\end{tabular}
  \caption{\todo{WRITE-ME}}
  \label{tab:exact_cvp}
\end{table}

>>>>

The LCG have been largely studied. This is why we know techniques to recover internal states knowing only upper or lower bits of the output, see \cite{Boyar1989}. A particular LCG is the Lehmer's generator \cite{Lehmer}, where the multiplier \(a\) is known and the increment is zero.

@@

To compute \(\lambda_1(L)\), we find the shortest vector of L thanks to an exact SVP solver (SVP stands for Shortest Vector Problem) and we compute its norm.

In this article, we will only use an exact CVP solver when \(k = 128-\ell\) and when we know the \(6\) upper bit of our Lehmer's generator. Hence \(\lVert T-U \rVert \leqslant \sqrt{n}2^{122-\ell} \). So, if we fix \(\ell\) we can search for the minimum \(n\) such that \[2\sqrt{n}2^{122-\ell} \leqslant \lambda_1(L(128-\ell,n))\].

\begin{table}
  \centering
    \begin{tabular}{|c|c|}
	\hline
	\(\ell\)  & minimum \(n\) \\
	\hline
	0  & 42 \\
	11 & 39 \\
	12 & 38 \\
	13 & 38 \\
	\hline
\end{tabular}
  \caption{\todo{WRITE-ME}}
  \label{tab:exact_cvp}
\end{table}
